---
title: "Data Science"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

BIOSTATISTICS is the nexus of two distinct disciplines - mathematical sciences and data science. The mathematical sciences forms the theory of biostatistics and enables meaningful conlusions to be drawn, and data science is a tool which translates real-world noise into useful guidance for decision-makers and policy experts. In essence, in the journey of biostatistics, math is the GPS and data science in the vehicle.

The following are a few examples of the work I've done in the world of data science.

### Instacart and Human Behavior

```{r libraries and output setup}
library(tidyverse)
library(plotly)
library(p8105.datasets)
```

```{r import the data}
#
#view(instacart_df)

data("instacart")

instacart_df = 
  instacart %>% 
  as_tibble()

instacart_df
```

Let's investigate the impulsive of humans by focusing on at the hour at which alcohol orders are placed.

```{r filtering the data}
instacart_impuslivity_df = 
  
  instacart_df %>% 
  
  select(order_hour_of_day, product_name, aisle, department, add_to_cart_order, days_since_prior_order) %>% 
  
  filter(department == "alcohol") %>% 
  
   mutate(aisle = recode(aisle,
                        "beers coolers" = "Beer",
                        "red wines" = "Red Wine",
                        "specialty wines champagnes" = "Specialty Wines and Champagnes",
                        "spirits" = "Spirits",
                        "white wines" = "White Wine"
                        )
         ) 

instacart_impuslivity_df
```

```{r}
instacart_impuslivity_df %>%
  
  mutate(text_label = str_c("Product: ", product_name, "\nDays Since Prior Order: ", days_since_prior_order)) %>% 
  
  plot_ly(
          x = ~order_hour_of_day, 
          y = ~add_to_cart_order, 
          color = ~aisle, 
          text = ~text_label, 
          alpha = 0.35,
          type = "scatter"
          )
```

```{r}
instacart_impuslivity_boxplot = 
  
  instacart_impuslivity_df %>% 

  plot_ly(
          x = ~days_since_prior_order, 
          y = ~aisle,
          color = ~aisle,
          type = "box"
          )

instacart_impuslivity_boxplot
```

[Return Home](index.html)

